---
title: "Adveq  map application"
author: "Amine Gassem"
date: "November 26, 2015"
output: 
  pdf_document: 
    toc: yes
---

----------------

# OVERVIEW

This document is a specification document. 

# GOALS

Within R and shiny framework , create a shiny application to display adveq global investments multiple and FMV on a global map per country or region. 

1. Create adveq map package `adveqmap`(choose better busniess . This package is the business layer. 
Contains all data and computations financial functions and objects.
2. Create a shiny application: `adveqmapshiny` this the package viewer. Internally the shiny app uses `adveqmap` package. 

Note that we isolate the busniess layer from view layer, this will :

* Better test and documentation. In fact, the workflow to test and document a package is clear but now way to do this for a shiny application (even if you can add comments to the code)
* The shiny application can be enhanced later to include many other packages.
* For advanced user , it is faster to have all busniess in a package ,no need to launch the shiny application. 

# SPECIFICATIONS

Adveq investment will be displayed in the map according  to the *Investment multiple*. The latter can be defined as for each geography $g$

$$ I^g_{multiple} = \frac{V_T^g}{C_T^g} $$
Where:

* $g$ can be a country or a region.
* $V_T^g$ is the sum of value over all the companies of the selected region:  $$V_T^g=\sum_{i \in Comp_g}{v_i}$$
* $C_T^g$ is the sum of cost over all the companies of the selected region:  $$C_T^g=\sum_{i \in Comp_g}{c_i}$$



# MILESTONES

We try here to give the details of future development. Development is divided in different milestone.
Each milestone contains a set of R function/tasks to do. The list is not exhaustive or definitive. 

## M1 : `adveqmap` package

### 1. Init the  package

  - Prepare project as an R package
  - Set github 
  - Init tests. All functions will be tested (`testthat`) 
  - Init documentation using documented (`roxygen`)
  
### 2. Load data 

Data can be loaded from an Excel workbook:

```{r load_data,eval=FALSE}

db <- load_data(path,table,conn=NULL)

```
We can imagine that the data will be loaded later directly from a data base. 
For example from an `SQL server` data base

```{r load_data_db,eval=FALSE}
library(rsqlserver)
conn <- dbConnect()
db <- load_data(table,conn=conn)

```
the result `db` is a `data.table`

### 3. Clean data 

* Clean data ,remove extra columns
* Format dates , format numbers
* Extract regions/sub regions 


```{r clean_db,eval=FALSE}
db <- clean_data(db)
```

### 4. Compute investment multiple 

Compute busniess variable that will be used to color the map.

```{r investmultiple,eval=FALSE}
db <- invest_multiple(db)
```

### 5. Create the map 

This the main function of the package.  Create a colorplate map.

```{r map,eval=FALSE}
map <- get_map(db)

```

## M2 `shiny` application

### 1. Init the shiny application 

* Create application hierarchy 
* Create user interface 
* Set github

### 2. Integrate the map to the application

Essentially here we call `adveqmap` functions. Either to show data or map.

* Develop the server part

### 3. Add app options 

* Add some filters 

Some function here can be moved to `adveqmap` package once they are stable.
The idea is to keep the shiny application as light as possible and with the minimum of business logic.


### 4. App deployment

* Deploy the application.
* Test functionalities within the server.


